Precision calculations of the cosmic shear power spectrum projection

### 2017-04-20 answer_to_referee.txt

We would like to thank the referee for their positive report and useful comments and suggestions.
Please fine below our replies to the referee's points. All modifications to the draft are highlighted
in red.

- Shear correlation function, eq. (47-48).
  We had indeed used a transformation (with the Legendre polynomial) that is incorrect for spin-2 correlations.
  We have replaced this with the correct transformations using the reduced Wigner D-matrices. We state their
  form in a new Appendix C. Figures 2 and 3, involving the shear correlation functions, have been updated
  accordingly.

- p. 6, chi-dependence of \tilde P_m.
  We added to the equation an approximate expression of P_m(k), without the chi-dependence. We hope that the
  subsequent text as it stands should make the conditions under which this approximation holds sufficiently clear.

- p. 7, accuracy of the ExtL2FlHyb.
  * Not sure about the reason. *

- Making Fig. 1 and following clearer.
  * Not sure that adding labels or anything else would make those clearer. *

- Table 1, extra column.
  We added columns indicating the ell_x such that for ell>ell_x the power spectrum projection has better
  accuracy than x, with x=10% and 1%.

- Fig. 3, comparison for xi_-.
  This plot has been updated, both xi_+ and xi_- are now compared to the full spherical case.

- Table 2, adding plot.
  * Really necessary? *

- Conclusions
  * I think present tense is fine *

- Fig. 4.
  * On my screen I don't have a problem with this figure. *

Other modifications.

- End of introduction: Lemos et al. reference added.

- Eq. 47: The definitions as <gamma gamma^*> and <gamma gamma> for xi_+ and xi_- have been added here,
  moved from eq. 48.

- Typos:
  All typos have been fixed.

### 2017-04-20 cfhtlens.tex
First draft of referee reply and modifications.

biases would {\it reduce} the recovered amplitude of $\sigma_8$ by $\sim

@@

@@

For a first-order standard Limber flat-sky approximation (L1Fl) we find
$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$, the same
result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
extended Limber flat-sky hybrid approximation (ExtL2FlHyb) results in $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} = 0.788 \pm 0.032$, a negligible change of the
amplitude that is well within the Monte-Carlo sampling noise. The largest
difference is measured with the depreciated case ExtL1Fl, for which the
recovered amplitude is larger by $16\%$ of the statistical error. These
negligible changes to the error bars were to be expected owing to the high
level of statistical noise and cosmic variance in comparison to the low-level
impact of the various approximations shown in Fig.~\ref{fig:Cl_cases}.

Table \ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
$\sigma_8 \Omega_{\rm m}^{0.6}$ for the various approximations to the
lensing power spectrum projections listed in Table~\ref{tab:cases} Note again
that these values do not represent the state-of-the-art cosmological results,
since many of the above listed analysis advancements made since 2013 have not
been taken into account. As an example of a significant effect, when using the
revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
\cite{2003MNRAS.341.1311S}, there is a decrease of $0.6 \sigma$ with $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} =0.768^{+0.029}_{-0.031}$.

>>>>

biases would {\it reduce}\/ the recovered amplitude of $\sigma_8$ by $\sim

@@

%\

@@

For a first-order standard Limber flat-sky approximation (L1Fl) we find
$\sigma_8 (\Omega_{\rm m}/0.27)^{0.6} =0.787^{+0.031}_{-0.033}$, the same
result that was published in \cite{CFHTLenS-2pt-notomo}. Using the second-order
extended Limber flat-sky hybrid approximation (ExtL2FlHyb) results in $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} = 0.788 \pm 0.032$, a negligible change of the
amplitude that is well within the Monte-Carlo sampling noise. The largest
difference is measured with the \forref{depreciated} case ExtL1Fl, for which the
recovered amplitude is larger by $16\%$ of the statistical error. These
negligible changes to the error bars were to be expected owing to the high
level of statistical noise and cosmic variance in comparison to the low-level
impact of the various approximations shown in Fig.~\ref{fig:Cl_cases}.

Table~\ref{tab:CFHTLenS_Sigma8} lists the mean and 68\% credible interval for
$\sigma_8 \Omega_{\rm m}^{0.6}$ for the various approximations to the
lensing power spectrum projections listed in Table~\ref{tab:cases}. Note again
that these values do not represent the state-of-the-art cosmological results,
since many of the above listed analysis advancements made since 2013 have not
been taken into account. As an example of a significant effect, when using the
revised non-linear power spectrum of \cite{2012ApJ...761..152T} in place of
\cite{2003MNRAS.341.1311S}, there is a decrease of $0.6 \sigma$ with $\sigma_8
(\Omega_{\rm m}/0.27)^{0.6} = 0.768^{+0.029}_{-0.031}$\forref{, using L1Fl}.
